Rigidity of Expectation Formation: Additional Evidence from Desntify Forecasts

### 2019-06-26 paper/Draft.tex
Finalized VarOtherMoments Figures

\begin{figure}[h]\label{UnceratitnyOtherMoments}
	\centering
		\centering
	\smallskip
	\includegraphics[width=3.5cm]{figures/Inf_var2Q.png}
	\includegraphics[width=3.5cm]{figures/fe_var2Q.png}
	\includegraphics[width=3.5cm]{figures/var_disg2Q.png}\\
	\smallskip
	\includegraphics[width=3.5cm]{figures/Inf_var3Q.png}
	\includegraphics[width=3.5cm]{figures/fe_var3Q.png}
	\includegraphics[width=3.5cm]{figures/var_disg3Q.png}\\
	\smallskip	
	\includegraphics[width=3.5cm]{figures/Inf_var.png}
	\includegraphics[width=3.5cm]{figures/fe_var.png}
	\includegraphics[width=3.5cm]{figures/var_disg.png}\\
		\caption{Unceratinty and Other Moments}
\end{figure}

@@

\begin{adjustbox}{width={22cm},totalheight={12cm},angle=90}\label{WeakRevEfficiency}
	\begin{tabular}{llllllllllllll}
		& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       &                      & \multicolumn{4}{l}{SCE}                           \\
		\multicolumn{14}{l}{Test 3. Weak revision efficiency of change in forecast}                                                                                                                                    \\
		& Mean change & t-1       & t-1- t-2  & t-1-t-3   & Mean revision & t-1       & t-1- t-2  & t-1-t-3   &                      & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
		L.InfExp\_Mean\_ch   &             & -0.295*** & -0.344*** & -0.367*** &               & -0.303*** & -0.348*** & -0.364*** & L.InfExp\_Var\_ch    &               & -0.382*** & -0.565*** & -0.652*** \\
		&             & (0.034)   & (0.044)   & (0.045)   &               & (0.043)   & (0.059)   & (0.062)   &                      &               & (0.015)   & (0.022)   & (0.037)   \\
		L2.InfExp\_Mean\_ch  &             &           & -0.179*** & -0.242*** &               &           & -0.162*   & -0.200**  & L2.InfExp\_Var\_ch   &               &           & -0.300*** & -0.406*** \\
		&             &           & (0.047)   & (0.049)   &               &           & (0.061)   & (0.067)   &                      &               &           & (0.021)   & (0.031)   \\
		L3.InfExp\_Mean\_ch  &             &           &           & -0.097**  &               &           &           & -0.088*   & L3.InfExp\_Var\_ch   &               &           & -0.123*** & -0.265*** \\

@@

		&             &           &           &           &               &           &           &           &                      &               &           &           & (0.025)   \\
		&             &           &           &           &               &           &           &           &                      &               &           &           & (0.018)   \\
		&             &           &           &           &               &           &           &           &                      &               &           &           & (0.012)   \\
		Constant               & -0.005      & -0.004    & -0.011    & -0.015    & 0.001         & 0.008     & -0.002    & -0.007    & Constant               & -1.339***     & -1.324*** & -1.139*** & -0.839*** \\
		& (0.023)     & (0.024)   & (0.026)   & (0.026)   & (0.020)       & (0.020)   & (0.022)   & (0.022)   &                      & (0.123)       & (0.110)   & (0.104)   & (0.163)   \\

@@

	$R^2$                  & 0.000       & 0.086     & 0.112     & 0.128     & 0.000         & 0.090     & 0.112     & 0.120     & $R^2$ & 0.000         & 0.182     & 0.278     & 0.321     \\

@@

FIRE predicts zero disagreements while both SE and NI models imply disagreements pick up following shocks regardless of the sign and gradully drop over longer horizon.  Looking into the graph, the average response of disgreements to the absolute value of technology and oil shocks does exhibite a pattern similar to the later.  Note now that the initial response is not statistically significant(same as the original result.). Besides, there is also one subtle difference between the SE and NI on disagreements in that disagreements always exist with the presense of private signals, in contrast, SE predicts that the disagreements is zero over the long run. The evidence from impulse response of disagreements seem to be more consistent with SE than NI.

>>>>

\begin{figure}[h]\label{UnceratitnyOtherMoments}
	\centering
		\centering
	\smallskip
	\includegraphics[width=3.5cm]{figures/Inf1yf_CPIAU_varSPFCPIQ.png}
	\includegraphics[width=3.5cm]{figures/SPFCPI_FE_varSPFCPIQ.png}
	\includegraphics[width=3.5cm]{figures/CPI_disg_varSPFCPIQ.png}\\
	\smallskip
	\includegraphics[width=3.5cm]{figures/Inf1yf_PCE_varSPFPCEQ.png}
	\includegraphics[width=3.5cm]{figures/SPFPCE_FE_varSPFPCEQ.png}
	\includegraphics[width=3.5cm]{figures/PCE_disg_varSPFPCEQ.png}\\
	\smallskip	
	\includegraphics[width=3.5cm]{figures/Inf1yf_CPIAU_varSCEM.png}
	\includegraphics[width=3.5cm]{figures/SCE_FE_varSCEM.png}
	\includegraphics[width=3.5cm]{figures/Q9_disg_varSCEM.png}\\
		\caption{Unceratinty and Other Moments}
\end{figure}

@@

\begin{adjustbox}{width={22cm},totalheight={12cm},angle=90}\label{WeakRevEfficiency}
	\begin{tabular}{llllllllllllll}
		\hline 
		& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       &                      & \multicolumn{4}{l}{SCE}                           \\
		\hline 
		\multicolumn{14}{l}{Test 3. Weak revision efficiency of change in forecast}                                                                                                                                    \\
		\hline 
		& Mean change & t-1       & t-1- t-2  & t-1-t-3   & Mean revision & t-1       & t-1- t-2  & t-1-t-3   &                      & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
		\hline 
		L.InfExp\_Mean\_ch   &             & -0.295*** & -0.344*** & -0.367*** &               & -0.303*** & -0.348*** & -0.364*** & L.InfExp\_Mean\_ch  &         & -0.433*** & -0.586*** & -0.642*** \\
		&             & (0.034)   & (0.044)   & (0.045)   &               & (0.043)   & (0.059)   & (0.062)   &                    &         & (0.01)     & (0.013)    & (0.025)    \\

		L2.InfExp\_Mean\_ch  &             &           & -0.179*** & -0.242*** &               &           & -0.162*   & -0.200**  & L2.InfExp\_Mean\_ch &         &           & -0.336*** & -0.439*** \\

		&             &           & (0.047)   & (0.049)   &               &           & (0.061)   & (0.067)   &                                   &         &           & (0.018)    & (0.031)    \\
		L3.InfExp\_Mean\_ch  &             &           &           & -0.097**  &               &           &           & -0.088*   & L3.InfExp\_Mean\_ch &         &           & -0.143*** & -0.270*** \\

@@

		&             &           &           &           &               &           &           &           & L4.InfExp\_Mean\_ch &         &           &           & -0.183*** \\

		&             &           &           &           &               &           &           &           &                                 &         &           &           & (0.027)    \\
		&             &           &           &           &               &           &           &           & L5.InfExp\_Mean\_ch &         &           &           & -0.096*** \\
		&             &           &           &           &               &           &           &           &                      &         &           &           & (0.021)    \\
		&             &           &           &           &               &           &           &           & L6.InfExp\_Mean\_ch &         &           &           & -0.044**  \\
		&             &           &           &           &               &           &           &           &                                     &         &           &           & (0.013)    \\
		Constant               & -0.005      & -0.004    & -0.011    & -0.015    & 0.001         & 0.008     & -0.002    & -0.007    & Constant              & -0.055* & -0.034    & -0.001    & -0.002    \\
		& (0.023)     & (0.024)   & (0.026)   & (0.026)   & (0.020)       & (0.020)   & (0.022)   & (0.022)   &                                 & -0.023  & -0.023    & -0.028    & -0.033    \\

@@

	$R^2$                  & 0.000       & 0.086     & 0.112     & 0.128     & 0.000         & 0.090     & 0.112     & 0.120     & $R^2$ &  0.000       & 0.202     & 0.273     & 0.306   \\

@@

FIRE predicts zero disagreements while both SE and NI models imply disagreements pick up following shocks regardless of the sign and gradully drop over longer horizon.  Looking into the graph, the average response of disgreements to the absolute value of technology and oil shocks does exhibite a pattern similar to the later.  Note now that the initial response is no longer statistically significant(same as the original result.) and the pick-up of disagreement after both shocks seem to take place one quarter after the shock.

The level at whch disagreements converge over the long-run shed light upon one subtle difference between the SE and NI. Disagreements always exist in NI with the presense of private signals , in contrast, disagreements is zero over the long run. The evidence from impulse response of disagreements seem to be more consistent with SE than NI.
